An Efficient Forecasting Approach for the Real-Time Reduction of Boundary Effects in Time-Frequency Representations

### 2020-07-11 Notes/results.tex
code
notes

Finally, in order to verify the ability of {\sf BoundEffRed} to be implemented in real time, we evaluate the computation time required for each iteration of Algorithm~\ref{alg:boundary}, corresponding to the update of the boundary-free TF representation. This check is performed on the real-time SST of a 10-minute sample of the respiratory signal. As the SST is temporally sub-sampled by a ratio of 10, the update should not exceed $10/\fs=0.1$~sec. This is indeed the case, as no iteration lasted longer than xx sec on a 6-Core Xeon CPU running at 3.5~GHz and 64~GB of RAM.

@@

\begin{table}
\centering
\caption{PPG signal: averaged performance index of the boundary-free TF representations for different extensions.}
\begin{tabular}{|c||c|c|c|}
  \hline
   \multirow{2}{*}{Extension method} & \multicolumn{3}{c|}{Performance index $D$} \\
   \cline{2-4}
      & STFT & SST & ConceFT\\
   \hhline{|=#=|=|=|}
%   Without extension & $2.52\times 10^{-2}$ & $9.41\times 10^{-2}$ & $1.03\times 10^{-1}$ \\
%   \hline
   {\sf SigExt} & $0.774$ & $0.048$ & $X$ \\
   \hline
   Symmetric & $0.818$ & $0.059$ & $X$ \\
   \hline
   EDMD & $0.566$ & $0.038$ & $X$ \\
   \hline
   GPR & $0.735$ & $0.045$ & $X$ \\
   \hline
\end{tabular}
\label{tab:otd.ppg}
\end{table}

>>>>

Finally, in order to verify the ability of {\sf BoundEffRed} to be implemented in real time, we evaluate the computation time required for each iteration of Algorithm~\ref{alg:boundary}, corresponding to the update of the boundary-free TF representation. This check is performed on the real-time SST of a 10-minute sample of the respiratory signal. As the SST is temporally sub-sampled by a ratio of 20, the update should not exceed $20/\fs=0.2$~sec. This is indeed the case, as no iteration lasted longer than $0.17$ sec on a 6-Core Xeon CPU running at 3.5~GHz and 64~GB of RAM.

@@

\begin{table}
\centering
\caption{PPG signal: averaged performance index of the boundary-free TF representations for different extensions.}
\begin{tabular}{|c||c|c|c|}
  \hline
   \multirow{2}{*}{Extension method} & \multicolumn{3}{c|}{Performance index $D$} \\
   \cline{2-4}
      & STFT & SST & ConceFT\\
   \hhline{|=#=|=|=|}
%   Without extension & $2.52\times 10^{-2}$ & $9.41\times 10^{-2}$ & $1.03\times 10^{-1}$ \\
%   \hline
   {\sf SigExt} & $0.774$ & $0.048$ & $0.826$ \\
   \hline
   Symmetric & $0.818$ & $0.059$ & $1.393$ \\
   \hline
   EDMD & $0.566$ & $0.038$ & $0.850$ \\
   \hline
   GPR & $0.735$ & $0.045$ & $0.816$ \\
   \hline
\end{tabular}
\label{tab:otd.ppg}
\end{table}
